Choose a License

### 2025-02-12 choose_license.qmd
Follow-up from d5e2128
Don't cover data dictionary during
license choice. The data dictionary
is most likely only a derivative work
of the data and I would rather have
clear examples of own contributions
for this page.

So far, you took care to legally include works by others in your project folder.
Up next, you will free up your project for reuse.
This means ensuring that every bit (co-)authored by you in the project
is put under a free/open license.
It may be that your project (i.e., its files and folders) is not one work,
but rather consists of multiple works available under different licenses.
In that case, you need to indicate the license on a per-file or per-folder basis
(rather than choosing one for the whole project).
Sometimes, even different parts of a file might be subject to different licenses.
For the purpose of this tutorial,
we will consider the manuscript and the bibliography which you edited
as well as the data dictionary you created.

@@

In the following example, the edited manuscript files have been multi-licensed
under [AGPLv3][agpl] (or later) or (at option of the reuser) under [CC\ BY-SA\ 4.0][cc-by-sa],
while the bibliography, the data dictionary and its code are made available under CC0\ 1.0.

>>>>

So far, you took care to legally include works by others in your project folder.
Up next, you will free up your project for reuse.
This means ensuring that every bit (co-)authored by you in the project
is put under a free/open license.
It may be that your project (i.e., its files and folders) is not one work,
but rather consists of multiple works available under different licenses.
In that case, you need to indicate the license on a per-file or per-folder basis
(rather than choosing one for the whole project).
Sometimes, even different parts of a file might be subject to different licenses.
For the purpose of this tutorial,
we will consider the manuscript and the bibliography which you edited.

@@

In the following example, the edited manuscript files have been multi-licensed
under [AGPLv3][agpl] (or later) or (at option of the reuser) under [CC\ BY-SA\ 4.0][cc-by-sa],
while the bibliography is made available under CC0\ 1.0.
